On Secure Delegation of SampBQP with a Classical Client

### 2020-02-08 bqp.tex
Make compiliation pass
Implement some suggestions from Skype call

@@

\Ethan{See https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf for conventions. Mal. parties have stars, protos use Pi. Stuff like $r[(P(w), V )(1n ,(M, x, t))$ }

@@

\begin{protocol}{1-message $\QPIP_1$ protocol $\Pi_{MF} = (P_{MF}, V_{MF})$ for $\BQP$ language $L$ \Ethan{TODO use macros}}
	\label{proto:BQP}
	Common input: $x\in\set{0,1}^n$. 
	\begin{enumerate}
		\item The verifier generates $\Lambda \leftarrow \cV_1(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
		\Ethan{change $\cV_1$ to $\cV_{MF, 1}$}
		\item The prover generates a certificate state $\rho\leftarrow\cP_2(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier applies the measurement $\Lambda$ to $\rho$ qubit-by-qubit. Let $w \in \set{0,1}^n$ denote the measurement outcome. It verifies the measurement outcome and produces a decision  $o\leftarrow\cV_3(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cV_3$ is a classical polynomial-time algorithm.
	\end{enumerate}
\end{protocol}

@@

\begin{protocol}{Blind Protocol $\Pi_{blind} = (P_{blind}, V_{blind}$) for $\BQP$ \Ethan{Define and use macros later}}
	\label{proto:BlindBQP}
	Let $x\in\set{0,1}^n$.
	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cF$.
	\begin{enumerate}
		\item The verifier, on input $x$ generates $\Lambda$ using $\cV_1$ of \cref{proto:BQP}.
			On input $\Lambda$, it computes $\Lambda'$ using \cref{decodeMeasureOrder}.
			It computes $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, and $y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
			Finally, it sends $y$ and $evk$ to the prover
		\item The prover homomorphically evaluates $\cP_2$ of \cref{proto:BQP} on input $y$, generating $\sigma=\mathsf{QHE.Eval}(\cP_2, y)$.
			The prover sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming ciphertext $\sigma$ according to $\Lambda'$, getting $ct$
			It applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $w$.
			On input $w$, it applies $\cV_3$ of \cref{proto:BQP} and outputs its result.
	\end{enumerate}
\end{protocol}

As we will see in the theorems below, \protoref{BlindBQP} is a $\QPIP_1$, constant round, and blind protocol for $\BQP$ with negligible completeness and soundness.

\begin{thm}
	\cref{proto:BlindBQP} has negligible completeness and soundness, and is blind.
\end{thm}
\begin{prf}
	The completeness follows by inspection.
	For blindness, the only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.

	\Ethan{TODO PROOFREAD ME}
	\Ethan{Convention: malicious parties have stars}

	\Ethan{Don't use blackboard bold for provers/verifiers}

	Suppose for the sake of contradiction that some prover $\bbP_{blind}^*$ breaks the soundness of \cref{proto:BlindBQP}.

	Then we use it to construct a prover $\bbP_{MF}^*$ against the soundness guarantees in \cref{proto:BQP}.

	$\bbP_{MF}^*$ simulates \cref{proto:BlindBQP} as $(V_{blind}(x), P_{blind}^*)()$

	\Ethan{Fix interface; $P_{blind}^*$ expects some message from $V$}

	When $\bbP_{blind}^*$ sends $\sigma$, $\bbP_{MF}^*$ computes and sends $\rho=\mathsf{QHE.Dec}_{sk}(\sigma)$ to the verifier. \Ethan{Make observation that $P_{blind}^*$ has $sk$

	By assumption, $\bbV_{Blind}$ has a non-negligible chance to accept after receiving $\sigma$.
	When that happens, $\cV(w)=\cV(\Lambda(\rho))=Acc$.
	So $\bbV_{MF}$ has the same probability to accept after receiving $\rho$.
\end{prf}

@@

\Ethan{TODO PROOFREAD ME}
We give a high-level overview of the compiliation results.

\begin{protocol}{\Cref{proto:BlindBQP} compiled using Mahadev's measurement protocol}
	\label{proto:QPIP0BQP}
	\begin{enumerate}
		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, y$ the same way as in \cref{proto:BlindBQP}.
			On input $\Lambda'$, it generates $k, td$.
			It sends $k, evk, y$ to the prover.
		\item The prover, on inputs $k, evk, y$, generates classical ``commitment" $m$ and internal state $\ket{st}$.
			It sends $m$ to the verifier.
		\item The verifier sends the prover a public fair coin $c\in{0,1}$.
		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
		\item The verifier, on inputs $k, td, m, c, a, sk$, generates and outputs either $acc$ or $rej$.
	\end{enumerate}
\end{protocol}

>>>>

\def\MF{\mathsf{MF}}
\nc{\PiMF}{\ensuremath{\Pi_\MF}}
\nc{\VMF}{\ensuremath{V_\MF}}
\nc{\PMF}{\ensuremath{P_\MF}}
\nc{\PMFstar}{\ensuremath{P_\MF^*}}
\nc{\cVMF}[1]{\ensuremath{\cV_{\MF,#1}}}
\nc{\cPMF}[1]{\ensuremath{\cP_{\MF,#1}}}

\def\blind{\mathsf{blind}}
\nc{\Piblind}{\ensuremath{\Pi_\blind}}
\nc{\Vblind}{\ensuremath{V_\blind}}
\nc{\Pblind}{\ensuremath{P_\blind}}
\nc{\Pblindstar}{\ensuremath{P_\blind^*}}
\nc{\cVblind}[1]{\ensuremath{\cV_{\blind,#1}}}
\nc{\cPblind}[1]{\ensuremath{\cP_{\MF,#1}}}

@@

\Ethan{See https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf for conventions. Mal. parties have stars, protos use Pi. Stuff like $r(P(w), V )(1n ,(M, x, t))$ }

@@

\begin{protocol}{1-message $\QPIP_1$ protocol $\PiMF = (\PMF, \VMF)$ for $\BQP$ language $L$}
	\label{proto:BQP}
	Common input: $x\in\set{0,1}^n$. 
	\begin{enumerate}
		\item The verifier generates $\Lambda \leftarrow \cVMF{1}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
		\item The prover generates a certificate state $\rho\leftarrow\cPMF{2}(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier applies the measurement $\Lambda$ to $\rho$ qubit-by-qubit.
			Let $w \in \set{0,1}^n$ denote the measurement outcome.
			It verifies the measurement outcome and produces a decision $o\leftarrow\cVMF{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVMF{3}$ is a classical polynomial-time algorithm.
	\end{enumerate}
\end{protocol}

@@

\begin{protocol}{Blind protocol $\Piblind = (\Pblind, \Vblind)$ for $\BQP$}
	\label{proto:BlindBQP}
	Let $x\in\set{0,1}^n$ be an input for $\Vblind$.
	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPMF{2}$.
	\begin{enumerate}
		\item The verifier generates $\Lambda\leftarrow\cVMF{1}(x)$.
			On input $\Lambda$, it computes $\Lambda'$ using \cref{decodeMeasureOrder}.
			Then it generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$ and $y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
			It sends $y$ and $evk$ to the prover.
		\item The prover homomorphically evaluates $\cPMF{2}$ on input $y$, generating $\sigma\leftarrow\mathsf{QHE.Eval}(\cPMF{2}, y)$.
			It sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier generates $ct\leftarrow\Lambda'(\sigma)$,
			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct)$,
			and then $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
			It outputs $o$.
	\end{enumerate}
\end{protocol}

As we will prove, $\Piblind$ is a $\QPIP_1$, constant round, and blind protocol for $\BQP$ with negligible completeness and soundness.

\begin{thm}
	$\Piblind$ has negligible completeness and soundness, and is blind.
\end{thm}
\begin{prf}
	The completeness follows by inspection.
	For blindness, the only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.

	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ violating the soundness guarantees of $\Piblind$,
	then we can use it to construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$.

	\Ethan{This construction is too small for a separate box but maybe still be too big to just write it like this?}

	We define $\PMFstar$ to first generate
	$$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}$$
	and
	$$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$$
	It then sends $y$ and $evk$ to $\Pblindstar$ and gets $\sigma$ back.
	Finally, it generates
	$$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$$
	and sends it to $\VMF$ qubit-by-qubit.

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.

	By assumption, $\Vblind$ has a non-negligible probability to accept after receiving $\sigma$.
	In other words, let $\Lambda\leftarrow\cVMF{1}$, and define $\Lambda'$ by \cref{decodeMeasureOrder},
	then with non-negligible probability
	$$\cVMF{3}(x, \Lambda, \widehat{\mathsf{QHE.Dec}_{sk}}(\Lambda'(\sigma))=acc$$
	which is equivalent to
	$$\cVMF{3}(x, \Lambda, \Lambda(\rho))=acc$$
	That is, $\PMFstar$ violates the soundness of $\PiMF$.
\end{prf}

@@

We give a high-level overview of the compiliation results.

\begin{protocol}{\Cref{proto:BlindBQP} compiled using Mahadev's measurement protocol \Ethan{Give this a name}}
	\label{proto:QPIP0BQP}
	\begin{enumerate}
		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, y$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
			On input $\Lambda'$, it generates $k, td$.
			It sends $k, evk, y$ to the prover.
		\item The prover, on inputs $k, evk, y$, generates classical ``commitment" $m$ and internal state $\ket{st}$.
			It sends $m$ to the verifier.
		\item The verifier sends the prover a public fair coin $c\in{0,1}$.
		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
		\item The verifier, on inputs $k, td, m, c, a, sk$, generates and outputs either $acc$ or $rej$.
	\end{enumerate}
\end{protocol}
